\documentclass[a4paper,10pt]{article}

% Packages
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    pdfborder={0 0 0},
    hidelinks
}

\geometry{margin=1.2cm}
\setlength{\columnsep}{1cm}
\titlespacing*{\section}{0pt}{6pt}{6pt}

% Colors
\definecolor{primary}{HTML}{004F9F}

% Section Title Style
\titleformat{\section}
  {\large\bfseries\color{primary}}
  {}
  {0pt}
  {}
  [\titlerule]

\begin{document}
\setlength{\parindent}{0pt}

% ---------------------- HEADER ----------------------
\begin{center}
    {\Huge \textbf{MAHADEVU M P}}\\[6pt]
    Mandya, India \,|\, +91 9008152398 \,|\, 
    \href{mailto:pmahadev592@gmail.com}{pmahadev592@gmail.com} \,|\, 
    \href{https://github.com/Devputta}{GitHub} \,|\, 
    \href{https://www.linkedin.com/in/mahadevu-m-p-58b51426b}{LinkedIn}
\end{center}

\vspace{8pt}

% SUMMARY
\section*{SUMMARY}
Highly motivated Data Analyst and aspiring Data Engineer with strong skills in Python, SQL, Power BI, automation, and data processing. Experienced in building dashboards, performing data cleaning, developing analytical solutions, automating workflows using RPA, and creating IoT-based systems with machine learning insights. Skilled at transforming raw data into meaningful insights to support data-driven decision-making.

\begin{multicols}{2}

% TECHNICAL SKILLS
\section*{TECHNICAL SKILLS}
Python, SQL, Java, C, Power BI, Power Pivot, DAX, Excel (Advanced), MySQL, Git, GitHub, MS Office, Jupyter Notebook,  
ETL Concepts, Data Cleaning, Data Visualization, Machine Learning Basics, Operating Systems, Computer Networks

\columnbreak

% PROFESSIONAL SKILLS
\section*{PROFESSIONAL SKILLS}
Strong analytical and system-thinking abilities. Skilled in workflow optimization and automation logic. Collaborative in Agile and team-based environments. Quick learner with strong adaptability to new technologies.

\end{multicols}

% EXPERIENCE
\section*{EXPERIENCE}

\textbf{Associate Intern – RPA \& Intelligent Automation (Remote)} \hfill Nov 2024 -- Mar 2025\\
\textit{Employability.life}\\
Developed automation solutions to streamline invoice-processing workflows. Built autonomous bots using UiPath to extract, classify, and validate invoice data. Integrated AI-based models to improve document interpretation accuracy and reduce manual effort. Enhanced operational efficiency through optimized workflows, validation rules, and reusable automation components.

\vspace{6pt}

\textbf{Data Analysis Intern (Remote)} \hfill Feb 2025 -- Apr 2025\\
\textit{VTU – Data Analysis Internship Program}\\
Gained practical experience in data cleaning, preprocessing, and exploratory data analysis. Worked with visualization tools to generate actionable insights. Developed skills in dashboard creation, reporting, and identifying trends within structured datasets.

% PROJECTS
\section*{PROJECTS}

\textbf{IoT-Based Automatic Water Monitoring System} \href{https://tarce.co/index.php/tarce/article/view/4261}{\textbf{- PUBLISH}} 
\hfill Nov 2024 -- Ongoing 2025\\
Developed a smart water monitoring system using ESP32, IoT sensors, and Blynk for real-time level tracking. Integrated machine learning models for water consumption analysis and anomaly detection.

\vspace{6pt}

\textbf{Interactive Sales \& Revenue Dashboard (Power BI)} \hfill Sep 2025\\
Designed a dynamic Power BI dashboard to analyze revenue, customer trends, and regional performance. Created DAX measures, drill-down visuals, and integrated multiple data sources.  
\emph{GitHub:} \href{https://github.com/Devputta/END-TO-END-DASHBOARD}{Dashboard Link}

\vspace{6pt}

\textbf{Insurance Policy Analytics Dashboard (Power BI)} \hfill Aug 2025 -- Sep 2025\\
Developed an insurance analytics dashboard tracking active/closed policies, claims, and premium performance. Implemented DAX metrics and interactive filters for business insights.  
\emph{GitHub:} \href{https://github.com/Devputta/DATAS-With-DaX}{Project Link}

% EDUCATION
\section*{EDUCATION}

\textbf{Bachelor of Engineering – Information Science} \\
PES College of Engineering, Mandya \hfill 2022 -- 2025 \\
CGPA: 7.79 / 10

\vspace{6pt}

\textbf{Diploma – Computer Science} \\
Government Polytechnic College, Ramanagara \hfill 2018 -- 2021 \\
Percentage: 78.99\%

% CERTIFICATIONS
\section*{CERTIFICATIONS}

\begin{itemize}[leftmargin=*]
    \item \textbf{HackerRank SQL \& Python} — Demonstrated strong SQL skills (joins, subqueries, grouping, analytical queries) and validated Python fundamentals including logic building and problem-solving. \href{https://www.hackerrank.com/certificates/e17870f3f8c5}{\textbf{LINK}}

    \item \textbf{Cyber Security Fundamentals – Zscaler} — Gained knowledge of OSI layers, subnetting, routing, tunneling, and hands-on network troubleshooting. \href{https://www.linkedin.com/posts/mahadevu-m-p-58b51426b_zscaler-eduskills-virtualinternship-activity-7335549278452404226-IAgV}{\textbf{LINK}}

    \item \textbf{Data Analysis – VTU} — Acquired practical skills in data cleaning, visualization, and extracting insights using analytical tools.
\end{itemize}

\end{document}
