\documentclass[a4paper,10pt]{article}

% Packages
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    pdfborder={0 0 0},
    hidelinks
}


\usepackage{fontawesome5}

\geometry{margin=1.2cm}
\setlength{\columnsep}{1cm}

% Colors
\definecolor{primary}{HTML}{004F9F}

% Section Title Style
\titleformat{\section}
  {\large\bfseries\color{primary}}
  {}
  {0pt}
  {}
  [\titlerule]

\begin{document}
\setlength{\parindent}{0pt}

% ---------------------- HEADER ----------------------
\begin{center}
    {\Huge \textbf{MAHADEVU M P}}\\[6pt]
    \faPhone\ ~+91 9008152398 \quad|\quad
    \faEnvelope\ \href{mailto:pmahadev592@gmail.com}{pmahadev592@gmail.com} \quad|\quad
    \faGithub\ \href{https://github.com/Devputta}{GitHub} \quad|\quad
    \faLinkedin\ \href{https://www.linkedin.com/in/mahadevu-m-p-58b51426b}{LinkedIn}
\end{center}

\vspace{8pt}

% SUMMARY
\section*{SUMMARY}
Highly motivated Python developer with expertise in building scalable, secure, and maintainable applications using Django. Experienced in designing and integrating APIs, collaborating in Agile environments, and implementing intelligent features using modern AI frameworks. Strong problem-solving mindset with excellent debugging skills, quick learning ability, and a focus on delivering production-ready solutions.

\begin{multicols}{2}

% TECHNICAL SKILLS
\section*{TECHNICAL SKILLS}
\textbf{Programming:} C, Java, Python\\[3pt]
\textbf{Databases:} MySQL\\[3pt]
\textbf{Core Concepts:} Operating Systems, Computer Networks, Software Testing\\[3pt]
\textbf{Tools:} Git, GitHub, Blynk, UiPath, MS Office\\[3pt]
\textbf{Soft Skills:} Leadership, Teamwork, Problem-Solving

\columnbreak

% PROFESSIONAL SKILLS
\section*{PROFESSIONAL SKILLS}
\begin{itemize}[leftmargin=0.4cm]
    \item Strong analytical and system-thinking ability
    \item Skilled in workflow optimization and automation logic
    \item Collaborative in Agile and team-based environments
    \item Fast learner with adaptability to new technologies
\end{itemize}

\end{multicols}

% EXPERIENCE
\section*{EXPERIENCE}

\textbf{Associate Intern – RPA \& Intelligent Automation} \hfill Nov 2024 -- Mar 2025\\
\textit{Employability.life}\\
Developed automation solutions to streamline invoice-processing workflows. Built autonomous bots using UiPath to extract, classify, and validate invoice data. Integrated AI-based models to enhance document interpretation accuracy and reduce manual effort. Improved operational efficiency through optimized design patterns, data-validation rules, and reusable automation components.

% PROJECTS
\section*{PROJECTS}

\textbf{IoT-Based Automatic Water Monitoring System} \href{https://tarce.co/index.php/tarce/article/view/4261}{- PAPER} \hfill Nov 2024 -- (On-going) 2025\\
Developed a smart water-monitoring system using ESP32, IoT sensors, and Blynk for real-time tracking. Integrated ML models for consumption analytics and anomaly detection.

\vspace{6pt}


\textbf{Hospital Management System} \href{https://github.com/Devputta/Hospital-Management-System}{- LINK} \hfill Jan 2024 -- Apr 2024\\
Created a web-based platform supporting appointment scheduling, doctor availability, and secure patient record management.

\vspace{6pt}

\textbf{Telegram Bot for College Information} \href{https://github.com/Devputta/my_college_info}{- LINK} \hfill Nov 2023 -- Jan 2024\\
Built a Python-based Telegram bot to provide instant access to timetables, ERP links, departmental details, and announcements.

% EDUCATION
\section*{EDUCATION}

\textbf{Bachelor of Engineering – Information Science} \\
PES College of Engineering, Mandya \hfill 2022 -- 2025 \\
CGPA: 7.79 / 10

\vspace{6pt}

\textbf{Diploma – Computer Science} \\
Government Polytechnic College, Ramanagara \hfill 2018 -- 2021 \\
Percentage: 78.99\%

% CERTIFICATIONS
\section*{CERTIFICATIONS}

\textbf{HackerRank SQL \& HackerRank Python} \href{https://www.hackerrank.com/certificates/e17870f3f8c5}{- LINK}\\
• Demonstrated strong SQL skills in joins, subqueries, grouping, and analytical queries; validated Python fundamentals including logic building and problem-solving.

\vspace{6pt}

\textbf{Cyber Security Fundamentals – Zscaler} \href{https://www.linkedin.com/posts/mahadevu-m-p-58b51426b_zscaler-eduskills-virtualinternship-activity-7335549278452404226-IAgV?utm_source=share&utm_medium=member_desktop&rcm=ACoAAEIbGzsB-Ck1TDOQDZkm_CeV1gAsWucQMlQ}{- LINK}\\
• Gained knowledge of OSI layers, subnetting, routing, tunneling, and hands-on network troubleshooting.

\vspace{6pt}

\textbf{Data Analysis – VTU}\\
• Acquired practical skills in data cleaning, visualization, and insight extraction using analytical tools.

\end{document}
