\documentclass[a4paper,10pt]{article}

% Packages
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    pdfborder={0 0 0},
    hidelinks
}

\geometry{margin=1.2cm}
\setlength{\columnsep}{1cm}

% Colors
\definecolor{primary}{HTML}{004F9F}

% Section Title Style
\titleformat{\section}
  {\large\bfseries\color{primary}}
  {}
  {0pt}
  {}
  [\titlerule]

\begin{document}
\setlength{\parindent}{0pt}

% ---------------------- HEADER ----------------------
\begin{center}
    {\Huge \textbf{MAHADEVU M P}}\\[6pt]
    Mandya, India | +91 9008152398 |
    \href{mailto:mahadevump657@gmail.com}{mahadevump657@gmail.com} |
    \href{https://github.com/Devputta}{GitHub} |
    \href{https://www.linkedin.com/in/mahadevu-m-p-58b51426b}{LinkedIn}
\end{center}

\vspace{8pt}

% SUMMARY
\section*{SUMMARY}
Highly motivated Python developer with expertise in building scalable, secure, and maintainable applications using Django. Experienced in designing and integrating APIs, collaborating in Agile environments, and implementing intelligent features using modern AI frameworks. Possesses strong problem-solving abilities, excellent debugging skills, quick learning capability, and a focus on delivering production-ready solutions.

\begin{multicols}{2}

% TECHNICAL SKILLS
\section*{TECHNICAL SKILLS}
C, Java, Python, MySQL, Operating Systems, Computer Networks, Software Testing, Git, GitHub, Blynk, UiPath, MS Office, Leadership, Teamwork, Problem-Solving

\columnbreak

% PROFESSIONAL SKILLS
\section*{PROFESSIONAL SKILLS}
Strong analytical and system-thinking abilities. Skilled in workflow optimization and automation logic. Collaborative in Agile and team-based environments. Fast learner with strong adaptability to new technologies.

\end{multicols}

% EXPERIENCE
\section*{EXPERIENCE}

\textbf{Associate Intern – RPA \& Intelligent Automation (Remote)} \hfill Nov 2024 -- Mar 2025\\
\textit{Employability.life}\\
Developed automation solutions to streamline invoice-processing workflows. Built autonomous bots using UiPath to extract, classify, and validate invoice data. Integrated AI-based models to improve document interpretation accuracy and reduce manual effort. Enhanced operational efficiency through optimized design patterns, data-validation rules, and reusable automation components.

% PROJECTS
\section*{PROJECTS}

\textbf{IoT-Based Automatic Water Monitoring System} \href{https://tarce.co/index.php/tarce/article/view/4261}{\textbf{- PUBLISH}} 
\hfill Nov 2024 -- (Ongoing) 2025\\
Developed a smart water-monitoring system using the ESP32, IoT sensors, and Blynk for real-time water-level tracking. Integrated ML models for consumption analytics and anomaly detection.

\vspace{6pt}

\textbf{Hospital Management System} \href{https://github.com/Devputta/Hospital-Management-System}{\textbf{- LINK}} 
\hfill Jan 2024 -- Apr 2024\\
Created a web-based platform for appointment scheduling, doctor availability tracking, and secure patient-record management.

\vspace{6pt}

\textbf{Telegram Bot for College Information} \href{https://github.com/Devputta/my_college_info}{\textbf{- LINK}} 
\hfill Nov 2023 -- Jan 2024\\
Built a Python-based Telegram bot that provides instant access to timetables, ERP links, departmental information, and announcements.

% EDUCATION
\section*{EDUCATION}

\textbf{Bachelor of Engineering – Information Science} \\
PES College of Engineering, Mandya \hfill 2022 -- 2025 \\
CGPA: 7.79 / 10

\vspace{6pt}

\textbf{Diploma – Computer Science} \\
Government Polytechnic College, Ramanagara \hfill 2018 -- 2021 \\
Percentage: 78.99\%

% CERTIFICATIONS
\section*{CERTIFICATIONS}

\textbf{HackerRank SQL \& HackerRank Python} \href{https://www.hackerrank.com/certificates/e17870f3f8c5}{\textbf{- LINK}}\\
• Demonstrated strong SQL skills including joins, subqueries, grouping, and analytical queries. Validated Python fundamentals including logic building and problem-solving.

\vspace{6pt}

\textbf{Cyber Security Fundamentals – Zscaler} \href{https://www.linkedin.com/posts/mahadevu-m-p-58b51426b_zscaler-eduskills-virtualinternship-activity-7335549278452404226-IAgV}{\textbf{- LINK}}\\
• Gained knowledge of OSI layers, subnetting, routing, tunneling, and hands-on network troubleshooting.

\vspace{6pt}

\textbf{Data Analysis – VTU}\\
• Acquired practical skills in data cleaning, visualization, and extracting insights using analytical tools.

\end{document}
